\bf Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2024-07-22 paper.qmd
Added second edge removal description

$$C_{h}^{(p)} = \frac{1}{n_h}\sum_{i =1}^{n_h} x_i, h = {1, \dots, b; n_h > 0}.$$
Furthermore, line segments that exist in the \kD{} model generate line segments in \pD{} by connecting the \pD{} means of the corresponding \kD{} bin centroids.

XXXAdd best fit with UMAP and discuss why it's the best fit

@@

XXX Should there be a second long edge removal? You can compute the edges in \pD{} now, and if there are long edges maybe these should be pruned, and we re-plot the \gD{} view.

>>>>

$$C_{h}^{(p)} = \frac{1}{n_h}\sum_{i =1}^{n_h} x_i, h = {1, \dots, b; n_h > 0}.$$
Furthermore, line segments that exist in the \kD{} model generate line segments in \pD{} by connecting the \pD{} means of the corresponding \kD{} bin centroids. If additional long edges need to be removed, compute the edges in \pD{} and pruned any detected long edges to improve the accuracy. Once pruned, re-plot the \gD{} view to ensure it accurately captures the data.

@@

<!-- XXX Should there be a second long edge removal? You can compute the edges in \pD{} now, and if there are long edges maybe these should be pruned, and we re-plot the \gD{} view.  -->

### 2024-07-22 paper.tex
Find the best model with UMAP and update the video link
Added second edge removal description

\[C_{h}^{(p)} = \frac{1}{n_h}\sum_{i =1}^{n_h} x_i, h = {1, \dots, b; n_h > 0}.\]
Furthermore, line segments that exist in the \kD{} model generate line
segments in \pD{} by connecting the \pD{} means of the corresponding
\kD{} bin centroids.

XXXAdd best fit with UMAP and discuss why it's the best fit

@@

\begin{minipage}{0.25\linewidth}
\includegraphics{figures/scurve/umap_trimesh_layout.png}\end{minipage}%
%
\begin{minipage}{0.25\linewidth}
\includegraphics{figures/scurve/sc_1.png}\end{minipage}%
%
\begin{minipage}{0.25\linewidth}
\includegraphics{figures/scurve/sc_2.png}\end{minipage}%
%
\begin{minipage}{0.25\linewidth}
\includegraphics{figures/scurve/sc_3.png}\end{minipage}%

\caption{\label{fig-scurve-sc}Model in \gD{}, on the UMAP layout, and
three views of the fit in projections from \(7\text{-}D\), for the
S-curve data (\((s_1, \ s_2) = (-0.160, \ -0.263)\),
\(b = 405 \  (15, \ 27)\), \(m = 70\), benchmark value to remove low
density hexagons is \(0.250\), and benchmark value to remove large edges
is \(0.159\)). MSE is \(0.0462\). The model closely fits the shape, but
it doesn't fully fill out the width of the S, which means that it does
not adequately capture the surface (The \textbf{langevitour} software is
used to view the data with a tour, and the full video is available at
\url{https://youtu.be/N6iWEj3aVps}).}

@@

XXX Should there be a second long edge removal? You can compute the
edges in \pD{} now, and if there are long edges maybe these should be
pruned, and we re-plot the \gD{} view.

>>>>

\[C_{h}^{(p)} = \frac{1}{n_h}\sum_{i =1}^{n_h} x_i, h = {1, \dots, b; n_h > 0}.\]
Furthermore, line segments that exist in the \kD{} model generate line
segments in \pD{} by connecting the \pD{} means of the corresponding
\kD{} bin centroids. If additional long edges need to be removed,
compute the edges in \pD{} and pruned any detected long edges to improve
the accuracy. Once pruned, re-plot the \gD{} view to ensure it
accurately captures the data.

@@

\begin{minipage}{0.25\linewidth}
\includegraphics{figures/scurve/umap_trimesh_layout.png}\end{minipage}%
%
\begin{minipage}{0.25\linewidth}
\includegraphics{figures/scurve/sc_umap_best_1.png}\end{minipage}%
%
\begin{minipage}{0.25\linewidth}
\includegraphics{figures/scurve/sc_umap_best_2.png}\end{minipage}%
%
\begin{minipage}{0.25\linewidth}
\includegraphics{figures/scurve/sc_umap_best_3.png}\end{minipage}%

\caption{\label{fig-scurve-sc}Model in \gD{}, on the UMAP layout, and
three views of the fit in projections from \(7\text{-}D\), for the
S-curve data (\((s_1, \ s_2) = (-0.160, \ -0.263)\),
\(b = 405 \  (15, \ 27)\), \(m = 70\), benchmark value to remove low
density hexagons is \(0.250\), and benchmark value to remove large edges
is \(0.159\)). MSE is \(0.0462\). The model closely fits the shape, but
it doesn't fully fill out the width of the S, which means that it does
not adequately capture the surface (The \textbf{langevitour} software is
used to view the data with a tour, and the full video is available at
\url{https://youtu.be/i7F7xpN1Hz8}).}

@@
